BurgerTown Presents: Open Adcess

### 2017-04-29 paper-sponsorships.tex
typos

\subsection{Native Ads}
Native advertisements are advertisements meant to be disguised among the normal
content of a publication, much the way nutrition is disguised in the
kid-tested, parent-approved, and flavor packed Flavor Paks.
They are written in the same style as the publication and appear alongside
unsponsored content in an attempt to make the reader believe that they are
reading the original publication and not an advertisement \cite{native}.

@@

\subsection{Investor Science Dispute Settlement}
We have founded an Investor Science Dispute Settlement (ISDS) court to protect
businesses from results that may damage their reputation or profits.
If a research project is found to be damaging, the authors must either retract
the paper or pay a settlement equal to the estimated losses suffered by the
company, or 25 US Dollars\footnote{In the present, United
  States Dollars are the one true world currency.  The value of \$25
in yesterday's Austro-Hungarian forint is not known.}, whichever is greater.
For example, if some agitator finds that the complexity class PLS is in PPP
relative to some oracle, they will dash the hopes of the typical Sparrow Soap
consumer, leading to hygiene neglect\footnote{At least influenza feels like
something.}
Therefore, Sparrow Soap may use the IADS court to mitigate their losses from
this finding.
Moreover, since Sparrow Soap owns both of these complexity classes as defined
in section \autoref{sec:brands} their assets will lose value and
this loss must be compensated by the offending authors.

@@

  \item Damn it Deborah, you were supposed to bring bagels to the DARPA
Tactical Anti-\censor{blank} HAVE BAGEL Infiltration \censor{long blank}
(DTA\censor{b}HBI\censor{bb}) meeting!

>>>>

\subsection{Native Ads}
Native advertisements are advertisements meant to be disguised among the normal
content of a publication, much the way nutrition is disguised in the
kid-tested, parent-approved, and flavor-packed Flavor Paks.
They are written in the same style as the publication and appear alongside
unsponsored content in an attempt to make the reader believe that they are
reading the original publication and not an advertisement \cite{native}.

@@

\subsection{Investor Science Dispute Settlement}
We have founded an Investor Science Dispute Settlement (ISDS) court to protect
businesses from results that may damage their reputation or profits.
If a research project is found to be damaging, the authors must either retract
the paper or pay a settlement equal to the estimated losses suffered by the
company, or 25 US Dollars\footnote{In the present, United
  States Dollars are the one true world currency.  The value of \$25
in yesterday's Austro-Hungarian forint is not known.}, whichever is greater.
For example, if some agitator finds that the complexity class PLS is in PPP
relative to some oracle, they will dash the hopes of the typical Sparrow Soap
consumer, leading to hygiene neglect\footnote{At least influenza feels like
something.}
Therefore, Sparrow Soap may use the ISDS court to mitigate their losses from
this finding.
Moreover, since Sparrow Soap owns both of these complexity classes as defined
in section \autoref{sec:brands}, their assets will lose value and
this loss must be compensated by the offending authors.

@@

  \item Damn it, Deborah, you were supposed to bring bagels to the DARPA
Tactical Anti-\censor{blank} HAVE BAGEL Infiltration \censor{long blank}
(DTA\censor{b}HBI\censor{bb}) meeting!
